A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-09-29 bioc-workflow.Rmd
move to Rnw, update license to CC-BY

---
title: "A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data"
author: "Lisa Breckels and Laurent Gatto"
output: pdf_document
---

@@

```{r qcbx, fig.width = 12} par(mfrow = c(1, 2)) o <-
order(hl$Iodixonal.Density) plotDist(hl[, o], pcol = "#00000010")
lines(colMeans(exprs(hl[, o])), col = "red", type = "b")
boxplot(exprs(hl[, o]), las = 2) ```

@@

```{r plotmarkers, fig.width = 12}
par(mfrow = c(1, 2))
plot2D(hl, main = "pRolocmarkers for mouse")
addLegend(hl, cex = .7)
plot2D(hl, dims = c(1, 7), main = "Marker resolution along PC 1 and 7")
```

@@

```{r plot2Drep, fig.width = 12} 
par(mfrow = c(1, 2)) 
plot2D(hl[, hl$Replicate == 1], main = "Replicate 1") 
plot2D(hl[, hl$Replicate == 2], main = "Replicate 2", mirrorX = TRUE) 
```

@@

```{r plotPDres, fig.width=9}
## Re-order the colours for the phenoDisco output
cl <- getMarkerClasses(hl, "pd")
cols <- getStockcol()[seq(cl)]
ind <- grep("Pheno", cl, invert = TRUE)
cols[ind] <- getStockcol()[seq(cl)][1:length(ind)]
cols[-ind] <- getStockcol()[seq(cl)][(length(ind) + 1):length(cl)]

@@

```{r visualiseOpt, eval=FALSE}
(best <- getParams(params))
plot(params)
levelPlot(params)
```
```{r visualiseOptHide, echo=FALSE, fig.width = 12}
library('gridExtra')
grid.arrange(plot(params), levelPlot(params), ncol = 2)
```

>>>>

@@

```{r qcbx}
par(mfrow = c(1, 2))
o <- order(hl$Iodixonal.Density)
plotDist(hl[, o], pcol = "#00000010")
lines(colMeans(exprs(hl[, o])), col = "red", type = "b")
boxplot(exprs(hl[, o]), las = 2)
```

@@

```{r plotmarkers}
par(mfrow = c(1, 2))
plot2D(hl, main = "pRolocmarkers for mouse")
addLegend(hl, cex = .7)
plot2D(hl, dims = c(1, 7), main = "Marker resolution along PC 1 and 7")
```

@@

```{r plot2Drep} 
par(mfrow = c(1, 2)) 
plot2D(hl[, hl$Replicate == 1], main = "Replicate 1") 
plot2D(hl[, hl$Replicate == 2], main = "Replicate 2", mirrorX = TRUE) 
```

@@

```{r plotPDres}
## Re-order the colours for the phenoDisco output
cl <- getMarkerClasses(hl, "pd")
cols <- getStockcol()[seq(cl)]
ind <- grep("Pheno", cl, invert = TRUE)
cols[ind] <- getStockcol()[seq(cl)][1:length(ind)]
cols[-ind] <- getStockcol()[seq(cl)][(length(ind) + 1):length(cl)]

@@

```{r visualiseOpt, eval=FALSE}
(best <- getParams(params))
plot(params)
levelPlot(params)
```
```{r visualiseOptHide, echo=FALSE}
library('gridExtra')
grid.arrange(plot(params), levelPlot(params), ncol = 2)
```
